---
title: "patrick"
author: "Patrick Shea"
date: "2025-09-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Patrick 

-   I am a twin ! My twin brother's name is Colin and he lives in Chicago.

-   My favorite places on the planet are river confluences. These three places are...

    -   The confluence of the Snake River and the Salmon River (Oregon/Idaho)

    -   The confluence of Green River and the Yampa River

    -   The Confluence of the Middle for of the Salmon with the Salmon (Idaho)

-   I went to college in Spokane, Washington.

-   My favorite books are *The Name of the Wind* by Patrick Rothufus, *All the Light We Cannot See* by Anthony Doer, and *A Sand County Almanac* by Aldo Leopold.

```{r}

```

```{r }




```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
